---
title: "MA615_Assignment_2"
author: "Chaoqun Yin"
date: "9/21/2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
library(tidyverse)
```

#R4DS Exercises

###3.5.1.2. What do the empty cells in plot with facet_grid(drv ~ cyl) mean? How do they relate to this plot?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(drv ~ cyl)

```
It means there is no valid data meeting the requirement of drv and cyl, that is, the number of cylinders and the way of driven. "
In this way, we can divide the data into specific groups with specific factors so we can compare the correlation of variables better."

###3.5.1.3. What plots does the following code make? What does . do?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)

```
The plot adds the third variable the way of driven on the row.
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)

```
The plot adds the third variable the number of cylinders on the column.


#Rewrite the shiny app
###Lake Huron
```{r}
#Load the data of Lake Huron
LakeHuron <- data.frame("year" = 1875:1972, "level" = LakeHuron)
#Plot broken line
ggplot(data = LakeHuron, aes(x <- year, y <- level)) +
  geom_line()
#Add smooth line
ggplot(data = LakeHuron, aes(x <- year, y <- level)) +
  geom_point() +
  geom_line() +
  geom_smooth()

```


